---
title: "jaenna_data_exploration"
author: "Jaenna Wessling"
date: "2023-02-28"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, warning = FALSE, message = FALSE)

library(here)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(patchwork)
library(kableExtra)
library(dplyr)
```

### Load in the new data

```{r}
days_exceed <- read_csv(here("Tab3_Days_ExceedHealthBenchmarks.csv"))

summary(days_exceed)

### By species 
### Days invert sed = max 381
### Days invertebrate water = max 250
### Days plant non-vascular = max 190 


### Days any species = max 381 (going to be from days invert sed
unique(days_exceed$huc)
```



### Plan of action
## Drop down menu to see days of exceedance by species & pesticide type 


### Wrangle by species

#### Fish
```{r}
fish <- days_exceed %>% 
  select(huc, days_fish, pesticide) %>% 
  slice_max(days_fish, n = 10) %>% # keeping the largest values of the counts by lake 
  arrange(-days_fish) # arranges selected choices from greatest to least 

## Plot it 
ggplot(data = fish, aes(y = days_fish, x = huc, fill = pesticide)) +  
  scale_x_discrete(limits = fish$huc) + 
  geom_col() +
  labs(y = 'Days of Exceedance', x = "Watershed",
       title = "Greatest Days of Exceedance for Fish Species") + 
  theme(axis.text.x = element_text(angle =75, hjust = 1))
```






#### Inverts water
```{r}
invert_water <- days_exceed %>% 
  select(days_invertebrate_water, pesticide, huc) %>% 
  slice_max(days_invertebrate_water, n = 10) %>% # keeping the largest values of the counts by lake 
  arrange(-days_invertebrate_water) # arranges selected choices from greatest to least 


## Plot it 
ggplot(data = invert_water, aes(y = days_invertebrate_water, x = huc, fill = pesticide)) +  
  scale_x_discrete(limits = invert_water$huc) + 
  geom_col() +
  labs(y = 'Days of Exceedance', x = "Watershed",
       title = "Greatest Days of Exceedance for Aquatic Invertabrate Species") + 
  theme(axis.text.x = element_text(angle =75, hjust = 1))
```


#### Inverts sediment
```{r}
invert_sed <- days_exceed %>% 
  select(days_invertebrate_sed, pesticide, huc) %>% 
  slice_max(days_invertebrate_sed, n = 10) %>% # keeping the largest values of the counts by lake 
  arrange(-days_invertebrate_sed) # arranges selected choices from greatest to least 


## Plot it 
ggplot(data = invert_sed, aes(y = days_invertebrate_sed, x = huc, fill = pesticide)) + 
  scale_x_discrete(limits = invert_sed$huc) + 
  geom_col() +
  labs(y = 'Days of Exceedance', x = "Watershed",
       title = "Greatest Days of Exceedance for Sediment Invertabrate Species") + 
  theme(axis.text.x = element_text(angle =75, hjust = 1))
```


#### Non-vascular plants 
```{r}
non_vasc_plant <- days_exceed %>% 
  select(days_plant_nonvascular, pesticide, huc) %>% 
  slice_max(days_plant_nonvascular, n = 10) %>% # keeping the largest values of the counts by lake 
  arrange(-days_plant_nonvascular) # arranges selected choices from greatest to least 

## Plot it 
ggplot(data = non_vasc_plant, aes(y = days_plant_nonvascular, 
                                  x = huc, 
                                  fill = pesticide,
                                  )) +  
  scale_x_discrete(limits = non_vasc_plant$huc) + 
  geom_col() +
  labs(y = 'Days of Exceedance', x = "Watershed",
       title = "Greatest Days of Exceedance for Non-Vascular Plant Species") + 
  theme(axis.text.x = element_text(angle =75, hjust = 1))
```

#### Vascular plants 
```{r}
vasc_plant <- days_exceed %>% 
  select(days_plant_vascular, pesticide,  huc) %>% 
  slice_max(days_plant_vascular, n = 8) %>% # keeping the largest values of the counts by lake 
  arrange(-days_plant_vascular) # arranges selected choices from greatest to least 


## Plot it 
ggplot(data = vasc_plant, aes(y = days_plant_vascular, 
                                  x = huc, 
                                  fill = pesticide,
                                  )) +  
  scale_x_discrete(limits = vasc_plant$huc) + 
  geom_col() +
  labs(y = 'Days of Exceedance', x = "Watershed",
       title = "Greatest Days of Exceedance for Vascular Plant Species") + 
  theme(axis.text.x = element_text(angle =75, hjust = 1))
```


#### All species
```{r}
all_species <- days_exceed %>% 
  select(days_any_species, pesticide, huc) %>% 
  slice_max(days_any_species, n = 10) %>% # keeping the largest values of the counts by lake 
  arrange(-days_any_species) # arranges selected choices from greatest to least 


## Plot it 
ggplot(data = all_species, aes(y = days_any_species, 
                                  x = huc, 
                                  fill = pesticide,
                                  )) +  
  scale_x_discrete(limits = all_species$huc) + 
  geom_col() +
  labs(y = 'Days of Exceedance', x = "Watershed",
       title = "Greatest Days of Exceedance for All Species") + 
  theme(axis.text.x = element_text(angle = 75, hjust = 1))
```

-------------------------------
### Old data set 

### Loading in the pesticides data to explore it 

#### Loading in watershed site pesticide and species RI
```{r}
# watershed_site_pesticide_species_ri <- read_csv(here("model_output_data", "BDW_NearHUC12_2015_2019_Watershed_Site_Pesticide_RI.csv"))
```


### Data exploration
```{r}
# summary(watershed_site_pesticide_species_ri)

# 18 variables
# 3 are characters
# The rest are numeric classes
# I don't see any NA values
```

### Data wrangling: Creating subsets of data for closer analysis
```{r}
## For my tab I am only interested in watershed site, pesticide type, and all of the species columns


# subset_pesticide_species <- watershed_site_pesticide_species_ri %>%
#   select(huc, pesticide, RI_max_fish:RI_max_net)
```

### Breaking data up by species
```{r, message=FALSE}
## Fish species
# fish_RI <- subset_pesticide_species %>%
#   select(huc, pesticide, RI_max_fish)
# 
# # ## Just want to see the highest RIs
# fish_RI_simplify <- fish_RI %>%
#   group_by(huc, pesticide) %>%
#   summarise(mean_RI = mean(RI_max_fish))
```


## Splitting up the huc sites for fish species
```{r, message=FALSE}
## Trying out group split in dplyr
# huc_fish_split <- group_split(fish_RI_simplify, huc)
## Doesn't properly name the new dfs though


## Using a for loop to further split up huc data
## Separating each huc into a different data frame
## Creating a vector for all of the unique huc ids
# hucs_fish <- unique(fish_RI_simplify$huc)
# 
# ## Turning the unique names output into a list
# huc_fish_id <- list()
# 
# 
# ## Looping through each of the unique huc values in the list and creating corresponding named data frames
# for(i in hucs_fish){
#      fish_RI_hucs <- paste0(i)
#      huc_fish_id[[fish_RI_hucs]] <- fish_RI_simplify[fish_RI_simplify$huc == i,]
# }
```


## Now that we have the data split, want to take the top 5 highest pesticide concentrations at each site
```{r, message=FALSE}
## Trying to lapply the slice max fcn to each subset...and failing
# for(i in huc_id){
#
#      lapply
# function (huc_id, FUN, ...)
# {
#     FUN <- slice_max(huc_id$mean_RI, n = 5)
#     .Internal(lapply(huc_id, FUN))
# }
# }
```



### Do the same process for each of these species
```{r}
## Invert water species
# invert_water_RI <- subset_pesticide_species %>%
#   select(huc, pesticide, RI_max_invertebrate_water)
# 
# 
# ## Separating by huc id / site
# ## Creating a vector for all of the unique huc ids
# hucs_inv_wtr <- unique(invert_water_RI$huc)
# 
# ## Turning the unique names output into a list
# huc_inv_wtr_id <- list()
# 
# 
# ## Looping through each of the unique huc values in the list and creating corresponding named data frames
# for(i in hucs_inv_wtr){
#      wtr_inv_hucs <- paste0(i)
#      huc_inv_wtr_id[[wtr_inv_hucs]] <- invert_water_RI[invert_water_RI$huc == i,]
# }
```

```{r}
## Plant non-vascular
# non_vasc_plant_RI <- subset_pesticide_species %>%
#   select(huc, pesticide, RI_max_plant_nonvascular)
# 
# ## Separating by huc id / site
# ## Creating a vector for all of the unique huc ids
# hucs_non_vasc <- unique(non_vasc_plant_RI$huc)
# 
# ## Turning the unique names output into a list
# huc_non_vasc_id <- list()
# 
# 
# ## Looping through each of the unique huc values in the list and creating corresponding named data frames
# for(i in hucs_non_vasc){
#      non_vasc_hucs <- paste0(i)
#      huc_non_vasc_id[[non_vasc_hucs]] <- non_vasc_plant_RI[non_vasc_plant_RI$huc == i,]
# }
```

```{r}
## Vascular plant
# vasc_plant_RI <- subset_pesticide_species %>%
#   select(huc, pesticide, RI_max_plant_vascular)
# 
# ## Separating by huc id / site
# ## Creating a vector for all of the unique huc ids
# hucs_vasc <- unique(vasc_plant_RI$huc)
# 
# ## Turning the unique names output into a list
# huc_vasc_id <- list()
# 
# 
# ## Looping through each of the unique huc values in the list and creating corresponding named data frames
# for(i in hucs_vasc){
#      vasc_RI_hucs <- paste0(i)
#      huc_vasc_id[[vasc_RI_hucs]] <- vasc_plant_RI[vasc_plant_RI$huc == i,]
# }
```

```{r}
## Invert benthic sediment
# sed_invert_RI <- subset_pesticide_species %>%
#   select(huc, pesticide, RI_max_invertebrate_sed)
# 
# ## Separating by huc id / site
# ## Creating a vector for all of the unique huc ids
# hucs_sed_invert <- unique(sed_invert_RI$huc)
# 
# ## Turning the unique names output into a list
# sed_invert_huc <- list()
# 
# 
# ## Looping through each of the unique huc values in the list and creating corresponding named data frames
# for(i in hucs_sed_invert){
#      sed_hucs <- paste0(i)
#      sed_invert_huc[[sed_hucs]] <- sed_invert_RI[sed_invert_RI$huc == i,]
# }
```

